US Korea Exchange Rates \\ STA206 Final Project

### 2014-12-11 paper.tex
set seed for preprocess test train split

    implemented local caching, decoupled download step
\end{verbatim}
The point is that through a little engineering the data analysis process
can be made transparent, automated, extensible, and fully reproducible.

>>>>

    implemented local caching, decoupled download step
\end{verbatim}

Through a little engineering the data analysis process
can be made transparent, automated, extensible, and fully reproducible.

Modern high level programming languages like R provide incredible tools. By
using their capabilities we can
